---
title: "How to Contribute to the Repository"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
source('./shared/html-utils.R')
git_user = 'dipterix'
```

Objectives:

A guide to add stuff to this repository

Table of contents:

* [Prerequisites](#pre-requisite)
* [Get started](#get-started)


### Pre-requisite

This website is built using `rmarkdown`. Please check the [guide](https://www.markdownguide.org/getting-started) if you don't know how to edit `markdown` files. To add/edit pages, you need `git` to get access to Github and `rmarkdown` installed. Luckily, these can all be found in `RStudio`. 

### Get Started

*This part is one-time setup*

1. Open RStudio, create project via `File` > `New Project` > `Version Control` > `Git`. Copy-paste `r sprintf("https://github.com/%s/owlserver", git_user)` into `Repository URL` and choose a proper directory.
```{r, echo=FALSE}
column(
  width = 9, offset = 3,
  thumbnail(title = 'Clone Git Repository', 
            img = 'shared/assets/images/import-repo.png', 
            caption = TRUE, width = 8)
)
```
2. Switch to `Terminal` tab in Rstudio, enter your Github user credentials like this:
```
$ git config --global user.name "Bob"
$ git config --global user.email "bob@example.com"
```
3. Run the following script to create your user. In my case, I created user `zw23`. Please change `user_name` to your name.
```
user_name = 'zw23'   # Change to your name here!!!

source('shared/template-utils.R')
add_user(user_name)
```
4. (Optional) In the opened `contributors.md`. Find the line just created, in my case, `* [Zw23](zw23.html)`, edit it so that others know who you are. (I changed mine to `* [Zhengjia](zw23.html)`)

### Create Your Pages

1. Create `.rmd` or `.md` file directly under **project** directory, the naming follows this convention:
```
user_name-article_topic-article_title.md
user_name-article_topic-article_title.rmd
```
Please use letters, digits and `_` for your username, article topics and title. Use `-` to link them.
2. (Optional) Run the following command to add your article into your personal site
```
source('shared/template-utils.R')
collect_user_topics(YOUR_USER_NAME)
```
3. Edit the file just created. If you want markdown references, check [a simple cheatsheet](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet) or the [source code of this page](https://github.com/dipterix/owlserver/blob/master/how-to-contribute-to-the-repository.Rmd)
4. Compile the site. There are two ways:
  a. run `rmarkdown::render_site()` in R
  b. *or*, Go to `Build` tab > `Build Website`
5. Pull, commit, and push to github: 
  * Go to `Git` tab in RStudio, select all files you want to save to Github, 
  * click `Commit`, add commit messages (description of what you did), 
  * press `commit`. If all goes well, you will see the following
  * Don't forget to press `Push`. This step actually send your local files to Github.
```{r, echo=FALSE}
column(
  12,
  thumbnail(title = 'Commit to stage your changes', 
            img = 'shared/assets/images/git-commit.png', 
            caption = TRUE, width = 6),
  thumbnail(title = 'Push to sync with Github repository', 
            img = 'shared/assets/images/git-push.png', 
            caption = TRUE, width = 6)
)
```
4. Preview your page, should be located at 
```{r} 
cat(sprintf("https://%s.github.io/owlserver/YOUR_FILE_NAME.html", git_user))
```

##### Notes

* If you want your markdown files to be compiled, don't create your markdown files under sub-folders, put them directly under project folder.
* Always `pull` > `commit` > `push` to avoid sync conflicts.
* Only allow letters, digits and `-`, `_` in your mardown file names, don't start with `_` nor `-`, otherwise the file will be marked **will not compile**.



