---
title: "Use Python on the Server"
author: "Zhengjia Wang"
date: "10/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Configure `Python` (version 2 and 3), installing conda etc.

* [Install Miniconda Step-by-step](#install-miniconda-step-by-step)
* [Create Python Virtual Environment](#create-python-virtual-environment)
* [Configure jupyter-notebook](#configure-jupyter-notebook)

#### Install Miniconda Step-by-step

Personally I highly recommend that you install `conda` environment as it usually saves tons of time managing different packages and dependencies. 

1. Open terminal, download `miniconda` to a temporary folder:
```
mkdir ~/junk
cd ~/junk
wget https://repo.anaconda.com/miniconda/Miniconda3-latest-Linux-x86_64.sh
```

2. Install 
```
sh Miniconda3-latest-Linux-x86_64.sh
```
  * hit `Enter` to read license agreement, you can press `shift+Q` and enter `yes` to agree
  * hit `Enter` to install conda to default location, and wait...
  * type `yes` to init conda

3. Setup start-up code

A quick way is:

```
echo "source ~/.bashrc" > ~/.bash_profile
```

4. Exit terminal and reconnect to the server. Now your prompt looks like `(base) -bash-4.2$ ...`. You can enter `conda list` to check whether conda is in your path.


#### Create Python Virtual Environment

1. Install conda, then enter
```
conda create -n py3 python=3
```

This will create a python3 environment called `py3`. If you have specific python version, please replace `python=3` with `python=3.x.x`.

You could also create python 2 environemnt to run old scripts

```
conda create -n py2 python=2
```

2. Activate environment

For example, I want to activate `py3` just created,
```
conda activate py3
```

Your prompt line will become `(py3) -bash-4.2$ `, this means you are in Python3 environment. You can check Python version using 
```
python -V
```

3. Install packages

Please use `conda install` as much as possible. For example, if you want to install GPU version of tensorflow:

```
conda install -c anaconda tensorflow-gpu
```

Here are some useful packages:

```
conda install jupyter h5py pandas hdf5 numpy ipykernel tensorflow-gpu
```

This will allow you to have jupyter notebook IDE.

#### Configure jupyter-notebook`

Finish the last two parts

1. Activate conda environment, generate config file
```
conda activate py3
jupyter notebook --generate-config
```

2. Create a password

In terminal, enter `python` to enter python command line.

Copy the following command

```
from notebook.auth import passwd; passwd()
```

Enter your password for jupyter notebook, repeat, and copy the somthing like `sha1:8ff338c59:f515cdc0b070eddae677238df5b3bcf9feefd` to your text editor.


3. Edit `~/.jupyter/jupyter_notebook_config.py`. 

If you don't know how to do that in command line, edit it in RStudio
```{r, eval = FALSE}
rstudioapi::navigateToFile('~/.jupyter/jupyter_notebook_config.py')
```

Find and change/uncommend these lines:

```
c.NotebookApp.allow_root = False

c.NotebookApp.open_browser = False

c.NotebookApp.notebook_dir = ''

# Enter your own hash code got from step 2 !!!
c.NotebookApp.password = 'sha1:bcd259ccf...<your hashed password here>'

c.NotebookApp.ip = '*'
c.NotebookApp.password_required = True
```

Save the file

4. Test `jupyter-notebook`

In terminal

```
jupyter notebook
```

The console will give you

```
[I 05:05:54.176 NotebookApp] Serving notebooks from local directory: ***
[I 05:05:54.176 NotebookApp] The Jupyter Notebook is running at:
[I 05:05:54.176 NotebookApp] http://[server name]:8888/
```

Copy the url above (starts with `http://`), copy into your browser.

Enter the password created from step 2.

```{r}
source('shared/html-utils.R')
thumbnail('Jupyter Notebook Login Screen', img = 'shared/assets/images/jupyter-login.png')
```

